---
title: "Using GRanges for Genome Annotations and Segments"
author: "Domenick J. Braccia"
date: "02/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is a document designed to investigate the presence of completely contained segments in 1000 bp bins within bacterial genomes. We used the [Bioconductor](www.bioconductor.org) package `GenomicRanges` to conduct this analysis.

First I will just start with getting used to the GRanges package

```{r, message=FALSE}
library(GenomicRanges)
library(GenomicFeatures)
library(rtracklayer)
library(ssh)
```


## Testing

```{r}
gr <- GRanges(
    seqnames = Rle(c("chr1", "chr2", "chr1", "chr3"), c(1, 3, 2, 4)),
    ranges = IRanges(101:110, end = 111:120, names = head(letters, 10)),
    strand = Rle(strand(c("-", "+", "*", "+", "-")), c(1, 2, 2, 3, 2)),
    score = 1:10,
    GC = seq(1, 0, length=10))
gr
```

## Making GRanges object from GFF files

Here, I am making GRanges object(s) for each genome and their annotation files from NCBI.

```{r}
# testing ssh package
session <- ssh_connect("dbraccia@cbcbsub01.umiacs.umd.edu")
tmp <- ssh_exec_internal(session, command = c("cd /fs/cbcb-lab/hcorrada/SGVFinder/SegmentAnalysis/", 
                                   "pwd"))
cat(rawToChar(tmp$stdout))
cat(rawToChar(tmp$stderr))

# initializations 
filenames <- list.files("../data/refseq_genome_annotations/")
genome_gffs <- list()

# importing all gff files into a list ## seq_along(filenames)
for (file in seq_along(filenames)) {
    #print(filenames[file])
    genome_gffs[[file]] <- import(paste0("../data/refseq_genome_annotations/", filenames[file]))
}
length(genome_gffs)

######################### TESTING IMPLEMENTATION ##############################
# call import()
track1 <- import("../data/refseq_genome_annotations/GCA_000005825.2_ASM582v2_genomic.gff")
track2 <- import("../data/refseq_genome_annotations/GCA_000005845.2_ASM584v2_genomic.gff")

# testing out GRangesList operations
track12_list <- list(track1, track2)
track12_GRList <- GRangesList(track12_list)
track12_GRList

# call makeGRangesFromDataFrame()

```

